SMASH companion source code repository

### 2019-03-14 analysis/index.Rmd
Updated LICENSE; updated main workflowr page.

> Zhengrong Xing and Matthew Stephens (2016). *Smoothing via Adaptive
Shrinkage (smash): denoising Poisson and heteroskedastic Gaussian
signals.* [arXiv:1709.10066][smash-preprint].

@@

The following analyses generate some of the empirical results
presented in [Xing & Stephens (2016)][smash-preprint]. If you
encounter a problem running any of the R code in these examples,
please post an [issue][issues].

@@

Copyright (c) 2016-2018, Zhengrong Xing, Peter Carbonetto & Matthew
Stephens.

@@

[smash-github]: https://github.com/stephenslab/smash-paper
[smashr]: https://github.com/stephenslab/smashr
[smash-preprint]: http://arxiv.org/abs/1605.07787
[issues]: https://github.com/stephenslab/smash-paper/issues
[mit-license]: https://opensource.org/licenses/mit-license.html
[wavelab]: http://statweb.stanford.edu/~wavelab
[waveden]: http://www-ljk.imag.fr/SMS/software/GaussianWaveDen/down.html
[zhengrong]: https://github.com/zrxing
[peter]: http://pcarbo.github.io
[matthew]: http://stephenslab.uchicago.edu

>>>>

> Zhengrong Xing, Peter Carbonetto and Matthew Stephens (2019).
> *Flexible signal denoising via flexible empirical Bayes shrinkage.*
> [arXiv:1605.07787][smash-preprint].

@@

The following analyses generate some of the empirical results
presented in [Xing, Carbonetto & Stephens (2019)][smash-preprint]. If
you encounter a problem running any of the R code in these examples,
please post an [issue][issues].

@@

Copyright (c) 2016-2019, Zhengrong Xing, Peter Carbonetto & Matthew
Stephens.

@@

[smash-github]: https://github.com/stephenslab/smash-paper
[smashr]: https://github.com/stephenslab/smashr
[smash-preprint]: https://arxiv.org/abs/1605.07787
[issues]: https://github.com/stephenslab/smash-paper/issues
[mit-license]: https://opensource.org/licenses/mit-license.html
[wavelab]: http://statweb.stanford.edu/~wavelab
[waveden]: http://www-ljk.imag.fr/SMS/software/GaussianWaveDen/down.html
[zhengrong]: https://github.com/zrxing
[peter]: http://pcarbo.github.io
[matthew]: http://stephenslab.uchicago.edu
